---
title: "Data Visualization Using mtcars dataset"
author: "Wichakorn Phuwasriwattananont"
date: "2024-03-02"
output:
  html_document: default
  pdf_document: default
---

# Create 5 charts by using 'mpg' dataset

## Call library
```{r}
library(tidyverse)
library(ggthemes)
library(patchwork)
library(scales)
```

## Prepare data
```{r}
# extrat gear types to new column 

mpg <- mpg %>% 
  mutate(gear = if_else(grepl("^auto", trans), "Auto", "Manual"))
```

## Prepare setting of title and axis's labels
```{r}
title_setting <- theme(axis.title = element_text(face="bold"),
                       plot.title = element_text(hjust = 0.5, face = "bold"))
```

## Q1: Correlation between Highway Miles per Gallon and City Miles per Gallon
```{r}
p1 <- ggplot(data = mpg,
       aes(x = cty, y = hwy)) + 
  geom_point(alpha = 0.2, color = "purple", size = 4) +
  geom_smooth(alpha = 0.3, color = "red", fill = "orange") +
  theme_minimal() +
  labs(title = "Highway Miles per Gallon vs City Miles per Gallon",
       y = "Highway Miles per Gallon",
       x = "City Miles per Gallon") + 
  title_setting
```
```{r, echo = FALSE}
print(p1)
```



## Q2: Highway Miles per Gallon for each Vehicle Classification 

```{r}
p2 <- ggplot(data = mpg,
       aes(x = hwy, y = reorder(class, hwy),
           fill = class)) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "Vehicle Classification vs Highway Miles per Gallon ",
       y = "Vehicle Classification",
       x = "City Miles per Gallon") +
  title_setting
```
```{r, echo = FALSE}
print(p2)
```

## Q3: Proprotion of gears in each manufacturer

```{r}
p3 <- ggplot(mpg, aes(y = manufacturer, fill = gear)) +
  geom_bar(position = "fill") +
  theme_minimal() +
  labs(title = "Manufacturer and Gear Types",
       x = "Proprotion") +
  title_setting
```
```{r, echo = FALSE}
print(p3)
```
## Q4: Proprotion of gears in whole manufacturer

```{r}

gear_n <- mpg %>% 
  select(gear) %>% 
  count(gear)

p4 <- ggplot(gear_n, aes(y = gear, x = n, fill = n)) +
  geom_col()  +
  theme_minimal() 
```
```{r, echo = FALSE}
print(p4)
```
## Q5: Difference of each vehicle classification in 9 years

```{r}
p5 <- ggplot(mpg, aes( y = class, x = as.character(year), col = class)) + 
  scale_size_area(max_size = 10) +
  geom_count() + 
  theme_minimal() 
```
```{r, echo = FALSE}
print(p5)
```

## Q6: Types of drive train of each manufacturer

```{r}
p6 <- ggplot(mpg,
       aes(y = manufacturer , fill = drv))+
  geom_bar(position = "fill")+
  theme_minimal()+
  scale_fill_brewer(palette = "Set2")+
  labs(
    title = "count-manufacturer-drv",
    caption = "mpg_table"
  )
```
```{r, echo = FALSE}
print(p6)
```

## Q7: Types of drive train and vehicle classification of each manufacturer

```{r}
p7 <- ggplot(mpg,
       aes(trans, manufacturer, col = class))+
  geom_count()+
  scale_size_area(max_size = 8) +
  theme_minimal()+
  labs(
    title = "Types of drive train and vehicle classification of each manufacturer")
```
```{r, echo = FALSE}
print(p7)
```

## Q8: Types of drive train and vehicle classification of each manufacturer

```{r}
p8 <- mpg %>% 
  select(class, hwy) %>% 
  group_by(class) %>% 
  summarise(average_hwy = mean(hwy)) %>% 
  ggplot(aes(x = average_hwy, y = reorder(class,average_hwy), fill = class)) +
  geom_col() +
  theme_minimal()
```
```{r, echo = FALSE}
print(p8)
```


